---
title: "simpleRegress"
author: "Jaelynn Schultz"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

The plot that relates the variables Length with Neck has a higher adjusted R_squared value when compared to the plot with the variables Length with Wieght. Length with Neck also produces a smaller residual standard error value (5.376 compared to 5.432). The variable "neck" appears to be the more accurate variable when trying to predict length. 


```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

In this graph, the residual standard error and adjusted r-squared values are too high/low when compared to the previous variables. This shows the relationship between a bears age and length is quite weak. 

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

The above scatterplot shows the relationship between length and headwth. This plot shows a higher residual standard error and a smaller adjusted r-squared when compared to the relationship between length and neck. 

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

The residual standard error and adjusted r-squared value with the variables of Length and Headlen better describes bear length in comparison to the plot illustrating the relationship between length and neck. 
